---
title: "Getting started with JsBarcode"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with JsBarcode}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

```{r setup}
library(JsBarcode)
```

`JsBarcode()` turns a value into an SVG barcode widget. Widgets render in the
RStudio viewer, in HTML documents such as this one, and in Shiny apps.

## Basic usage

The default symbology is CODE128, which accepts any ASCII text.

```{r}
JsBarcode("Hello world")
```

## Formats

Pick a symbology with `format`. All supported values are in `barcode_formats`:

```{r}
barcode_formats
```

```{r}
JsBarcode("5901234123457", format = "EAN13")
JsBarcode("123456789999", format = "UPC")
JsBarcode("CODE39 TEXT", format = "CODE39")
```

A value that is not valid for the chosen format produces an inline message
instead of a barcode:

```{r}
JsBarcode("not a number", format = "EAN13")
```

## Styling

```{r}
JsBarcode("ABC-123",
          bar_width = 3,
          bar_height = 60,
          line_color = "#1a4f8b",
          background = "#eef3fa",
          font_size = 16)

JsBarcode("NO-TEXT", display_value = FALSE, bar_height = 40)
JsBarcode("id-0042", text = "Custom label")
```

Any other [JsBarcode option](https://github.com/lindell/JsBarcode/wiki/Options)
can be passed through `...` using its JavaScript name:

```{r}
JsBarcode("Top text", textPosition = "top", textAlign = "left", font = "serif")
```

## Shiny

```{r, eval = FALSE}
library(shiny)

ui <- fluidPage(JsBarcodeOutput("code"))
server <- function(input, output) {
  output$code <- renderJsBarcode(JsBarcode("Hello Shiny"))
}
shinyApp(ui, server)
```

A full demo app ships with the package:

```{r, eval = FALSE}
shiny::runApp(system.file("examples/shiny", package = "JsBarcode"))
```
